Common Concerns in BYOD Policies

### 2016-12-16 paper.tex
updates

@@

@@

\section{Rule Structures and Checks}

@@

\section{Common Concerns}

@@

>>>>

\newcommand{\comment}[1]{}

@@

\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}

@@

\section{Rule Structures}

@@

\section{Common Concerns and Checks}
\label{sec:common_concerns}

Analyzing each of the policies common concerns become apparent.
We took care to ensure that our policies used the same predicates between themselves.
A summary of predicates used in multiple policies by our translation is given in \autoref{tab:common}.

Acknowledgements, and predicates linking devices to owners are used in all policies.
Most policies described rules for when device features should be enabled and disabled.
Configuring device features is a common feature to many MDM packages, but tracking what a user agrees to is not seen in leading MDM packages like MaaS360 or BES~\cite{rob_smith_magic_2016}.
Only 2 out of 5 policies had rules limiting what networks, servers, or access points a device could access;
  and only the two most complex policies had rules limiting what apps could be installed.
This is surprising as a common feature of MDM tools is controlling how devices and apps access networks.
User's have privacy preferences about apps~\cite{lin_modeling_2014}, but not all companies try and control what apps employees install.
Providing curated app stores and blacklisting apps is a feature common to many MDM programs.
Not all policies express opinions about apps however.

\begin{table}\sffamily\footnotesize\centering
\begin{tabular}{c c c c c c}
\toprule                        \\ 
Predicate                       & \rb{SANS} & \rb{HiMSS} & \rb{NHS} & \rb{Sirens} & \rb{Edinburgh} \\
\midrule
\comment 5  mustAcknowledged    &    \cmark & \cmark     &   \cmark & \cmark      &         \cmark \\
\comment 5  hasAcknowledged     &    \cmark & \cmark     &   \cmark & \cmark      &         \cmark \\
\comment 5  isOwnedBy           &    \cmark & \cmark     &   \cmark & \cmark      &         \cmark \\
\comment 5  isDevice            &    \cmark & \cmark     &   \cmark & \cmark      &         \cmark \\
\comment 4  mustDisable         &    \cmark &            &   \cmark & \cmark      &         \cmark \\
\comment 4  isLost              &    \cmark & \cmark     &   \cmark & \cmark      &                \\
\comment 4  isEmployee          &    \cmark &            &   \cmark & \cmark      &         \cmark \\
\comment 4  isApp               &    \cmark & \cmark     &   \cmark & \cmark      &                \\
\comment 4  isActivated         &    \cmark & \cmark     &   \cmark &             &         \cmark \\
\comment 3  mustEnable          &    \cmark & \cmark     &          & \cmark      &                \\
\comment 3  mustWipe            &           & \cmark     &   \cmark & \cmark      &                \\
\comment 3  isEncrypted         &    \cmark &            &   \cmark &             &         \cmark \\
\comment 3  hasMet              &    \cmark &            &   \cmark &             &         \cmark \\
\comment 3  canMonitor          &    \cmark &            &   \cmark & \cmark      &                \\
\comment 2  mustInform          &    \cmark &            &   \cmark &             &                \\
\comment 2  isTelephoneNumber   &    \cmark &            &   \cmark &             &                \\
\comment 2  isString            &           &            &   \cmark & \cmark      &                \\
\comment 2  isSecurityLevel     &    \cmark & \cmark     &          &             &                \\
\comment 2  isInstallable       &    \cmark &            &   \cmark &             &                \\
\comment 2  isFeature           &    \cmark &            &          & \cmark      &                \\
\comment 2  isData              &    \cmark &            &          & \cmark      &                \\
\comment 2  isApprovedFor       &           & \cmark     &   \cmark &             &                \\
\comment 2  isApproved          &    \cmark & \cmark     &          &             &                \\
\comment 2  hasFeature          &           &            &   \cmark &             &         \cmark \\
\comment 2  hasDevice           &           & \cmark     &   \cmark &             &                \\
\comment 2  hasDepartment       &           & \cmark     &          &             &         \cmark \\
\comment 2  canUse              &    \cmark &            &   \cmark &             &                \\
\comment 2  canStore            &    \cmark & \cmark     &          &             &                \\
\comment 2  canInstall          &    \cmark &            &   \cmark &             &                \\
\comment 2  canConnectToServer  &    \cmark &            &   \cmark &             &                \\
\comment 2  canConnectToNetwork &    \cmark &            &          & \cmark      &                \\
\comment 2  canConnectToAP      &    \cmark & \cmark     &          &             &                \\
\comment 2  canCall             &    \cmark &            &   \cmark &             &                \\
\comment 2  canBackupTo         &           & \cmark     &          &             &         \cmark \\
\bottomrule                     \\
\end{tabular}
\caption{Occurrences of predicates common to multiple policies.}
\label{tab:common}
\end{table}

All of the policies we looked at required employees to be aware of and acknowledge the existence of other policies.
The use of acknowledgements are noteworthy because the policies acknowledged may not be automatically enforcible.
These other rules include ethical or legal guidelines and disclaimers about data-loss.
Writing software to check a user is aware they may lose the data, and is behaving ethically may not be possible.

An aspect of acknowledgements is they require a delegation of trust from the company to their employees.
The employees have to be responsible for stating what they do or do not acknowledge.
Delegation is key to other policy decisions in the policies.
The IT department is delegated to audit apps.
Users are responsible for reporting their device missing.

We summarise the number (and percentage) of rules in the policies using acknowledgements and delegation relationships in \autoref{tab:summary}.
For comparison we also give the at the number of rules which describe some form of restriction.
Delegation relationships form a significant proportion of all the policies.
Acknowledgements are used extensively in the HiMSS policy, but rarely in the SANS policy.
Overall acknowledgements form as much a part of the policies as do device restrictions.
MDM software has focussed on implementing device restrictions and configurations; but it would seem that other aspects are equally important.

\begin{table}\centering\footnotesize\sffamily
\newcommand{\numpc}[2]{\scriptsize #1 (#2\%)}
  \setlength{\tabcolsep}{1pt}
  \begin{tabular}{l c c c c c}
    \toprule
                                   & \rb{SANS}      & \rb{HiMSS}     & \rb{NHS}       & \rb{Sirens}    & \rb{Edinburgh} \\
    \midrule                                                                                          
    Rules using acknowledgement    & \numpc{2}{6}   & \numpc{10}{67} & \numpc{11}{20} & \numpc{6}{24}  & \numpc{1}{5}   \\
    Rules using delegation         & \numpc{23}{70} & \numpc{5}{33}  & \numpc{33}{59} & \numpc{13}{52} & \numpc{2}{10}  \\
    Rules describing a restriction & \numpc{18}{54} & \numpc{3}{20}  & \numpc{8}{14}  & \numpc{5}{20}  & \numpc{1}{5}   \\
    \bottomrule                    \\
  \end{tabular}
  \caption{Summary of idioms in each of the policies.}
  \label{tab:summary}
\end{table}

@@

Each of the policies use delegation to describe rules.
A delegation requires at least two parties: someone to hand off the decision, and someone to hand the decision to.
SecPAL requires all statements be made by an explicit speaker.
When translating the policies into SecPAL we created a principal to deliver the policy.
In most cases we took the company (who had authored the document) as the speaker: however in the HiMSS policy rules are phrased as a user stating what they will do.
In the HiMSS case the user was the primary speaker.
